### 2020-02-29 ChapterBackground/chapterBackground.tex
Updated: Microservices for games

\section{Containerisation of Game Engines}
%Game engines, generally, currently run as one single application, including graphics, physics, AI etc. (with the exception of databases for user data). AP separates out the physics element into its own container, much like many modern systems are splitting up different aspects of systems into their own containers, for example web applications. This containerisation of physics, means, physics can be elastically scaled independently from other systems such as graphics, along with other advantages of modularity.

>>>>

\section{Microservices for Game Engines}
Microservices have gained much recent attention in the software industry in the context of cloud computing. The reason for this, is the microservice architecture allows for greater leverage of the opportunities that cloud computing presents. Additional advantages include flexible horizontal scaling, as well as more efficient team structures during development \cite{2017ExtractionofMicroservices}.

Popular existing commercial game engines, such as Unity \cite{Unity} and Unreal Engine \cite{Unreal} , are based on the Monolith architecture. However, for game engines to take greater advantage of cloud deployment a move to a microservice architecture will be needed. This would allow for independent horizontal scaling and resource provision management of the different systems within a game engine, such as graphics, physics and AI. Despite the recent commercial interest in microservice architecture, there has been no academic research into the use of microservices for game engines. The only notable exception to this is \cite{vaha2017applying}, however, this has a limited focus to the application of microservices to the genre of Massively Multiplayer Online Role-Playing Games (MMORPG).

A microservice architecture for a game engine would create a more cost efficient approach to cloud-hosted games and simulations, while also creating the potential for the scalability of individual systems on an on-demand basis. This study's problem is concentrated on separating out the physics system from the game engine and distributing it across multiple servers while maintaining the real-time streamed service to players. Through this distribution, this study aims to demonstrate that the physics aspect of a game engine can be horizontally scaled through the use of cloud computing.
